Towards automated provenance collection for experimental runs of agent-based models

### 2023-09-04 paper/paper.tex
Added expernses and finished presentation

%%% GP: to discuss -- which other authors should we include here?
%%% GP: Kit Macleod? (Has he had intellectual input into this via WP1?)
%%% GP: Coran Musk? (Random acknowledgement for looking after the machines)
%%% GP: Lorenzo Milazzo? (As the original SSREPI developer)
%%% GP: Dawn Parker? (As MIRACLE PI -- do we see this as a MIRACLE paper?)
%
\authorrunning{D. Salt et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{The James Hutton Institute, Craigiebuckler, Aberdeen, AB15 8QH, Scotland
\email{\{doug.salt,gary.polhill\}@hutton.ac.uk}\\
\url{https://www.hutton.ac.uk/}
\and Satellite and Surface Assimilation (SSA) Group
Met Office, FitzRoy Road, Exeter, Devon, EX1 3PB, UK
\email{lorenzo.milazzo@physics.org}
\and University of Waterloo, 200 University Avenue West
Waterloo, ON, Canada  N2L 3G1
\url{https://uwaterloo.ca/}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
    We demonstrate a working framework for the automatic recording of
    provenance and metadata for primarily agent-based models that could easily
    be adapted to the other modelling environments. We discuss the need for
    such a framework, the philosophy behind the design we adopted, the
    implementation, discuss the results and demonstrate a simple tool for for
    tracing bad data through a provenance graph.

\keywords{Provenance \and metadata \and modelling \and automation \and replication.}
\end{abstract}
%
%
%
\section{Introduction}

@@

\begin{figure} \includegraphics[width=\textwidth]{img/high-lit-provenance-trace.pdf}
\caption{A provenance sub-graph showing (in red) the propagation of bad data through the system} \label{fig:high-lit-provenance-trace} \end{figure}

>>>>

%%% GP: to discuss -- which other authors should we include here?
%%% GP: Kit Macleod? (Has he had intellectual input into this via WP1?)
%%% GP: Coran Musk? (Random acknowledgement for looking after the machines)
%%% GP: Lorenzo Milazzo? (As the original SSREPI developer)
%%% GP: Dawn Parker? (As MIRACLE PI -- do we see this as a MIRACLE paper?)
%
\authorrunning{D. Salt et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{The James Hutton Institute, Craigiebuckler, Aberdeen, AB15 8QH, Scotland
\email{\{doug.salt,gary.polhill\}@hutton.ac.uk}\\
\url{https://www.hutton.ac.uk/}
\and Satellite and Surface Assimilation (SSA) Group
Met Office, FitzRoy Road, Exeter, Devon, EX1 3PB, UK
\email{lorenzo.milazzo@physics.org}
\and University of Waterloo, 200 University Avenue West
Waterloo, ON, Canada  N2L 3G1
\url{https://uwaterloo.ca/}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
\    We demonstrate a working framework for the automatic recording of
    provenance and metadata for primarily agent-based models that could easily
    be adapted to the other modelling environments. We discuss the need for
    such a framework, the philosophy behind the design we adopted, the
    implementation, discuss the results and demonstrate a simple tool for for
    tracing bad data through a provenance graph.

keywords{Provenance \and metadata \and modelling \and automation \and replication.}
\end{abstract}
%
%
%
\section{Introduction}

@@

\begin{figure} \includegraphics[width=\textwidth]{img/high-lit-provenance-trace.pdf}
\caption{A provenance sub-graph showing (in red) the propagation of bad data through the system. Again we are being deliberately vague in order to give you an idea of the size and complexity of the graph} \label{fig:high-lit-provenance-trace} \end{figure}
